The Efficient Handling of Guards in the Design of RPython's Tracing JIT

### 2012-08-13 talk/vmil2012/paper.tex
typos

From Figure~\ref{fig:failing_guards} we can see that only a very small amount
of all the guards in the optimized traces ever fail. This amount varies between
2.4\% and 5.7\% of all guards. As can be expected, even fewer guards fail often
enough that a bride is compiled for them, only 1.2\% to 3.6\% of all guards
fail often enough that a bridge is compiled. Also of all failing guards a few fail extremely often
and most fail rarely. The results emphasizes that as most of the guards never
fail it is important to make sure that the successful execution of a guard does
not have unnecessary overhead.

>>>>

From Figure~\ref{fig:failing_guards} we can see that only a very small amount
of all the guards in the optimized traces ever fail. This amount varies between
2.4\% and 5.7\% of all guards. As can be expected, even fewer guards fail often
enough that a bridge is compiled for them, only 1.2\% to 3.6\% of all guards
fail often enough that a bridge is compiled. Also of all failing guards a few fail extremely often
and most fail rarely. The results emphasize that as most of the guards never
fail it is important to make sure that the successful execution of a guard does
not have unnecessary overhead.
